### 2013-10-05 Docs/MESA/instructions.tex
hook MESA chapter in
remove upquote in MESA/instructions.tex for now -- needs later latex

\item {\tt BLAS} and {\tt LAPACK}: Make sure the location of {\tt LAPACK} and 
{\tt BLAS} (provided with the {\sf MESA} source tree) are set using the 
following definitions (these should be the default settings):
\begin{lstlisting}[language=make,mathescape=false,upquote=true]
  WHICH_LAPACK = USE_SRCS
  LOAD_LAPACK = -lmesalapack
  WHICH_BLAS = USE_SRCS
  LOAD_BLAS = -lmesablas
  MKL_INCLUDE =
\end{lstlisting}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compile MESA on Hopper, a Cray XE6 machine
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Install {\sf MESA} on Hopper}
\label{sec:hopper_install}
\input hopper_compile

>>>>

\item {\tt BLAS} and {\tt LAPACK}: Make sure the location of {\tt LAPACK} and 
{\tt BLAS} (provided with the {\sf MESA} source tree) are set using the 
following definitions (these should be the default settings):
\begin{lstlisting}[language=make,mathescape=false]%,upquote=true]
  WHICH_LAPACK = USE_SRCS
  LOAD_LAPACK = -lmesalapack
  WHICH_BLAS = USE_SRCS
  LOAD_BLAS = -lmesablas
  MKL_INCLUDE =
\end{lstlisting}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compile MESA on Hopper, a Cray XE6 machine
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Install {\sf MESA} on Hopper}
\label{sec:hopper_install}
\input \mesafigpath/hopper_compile
